Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-21 lqg-strings.tex
Added acknowledgments

\begin{acknowledgments}

\end{acknowledgments}

>>>>

\begin{acknowledgments}
DV would like to thank Thomas van Riet for going over an early draft of this work and for his valuable comments. DV and LdS would both like to thank David Schmitt for his very valuable observations regarding the nature of the $\Delta$ field and its relation to the Kalb-Ramond field. Finally we would like to humbly dedicate this work to the memory of the victims of the genocide in Gaza.
\end{acknowledgments}
